% Example CV

\documentclass[11pt, a4paper]{moderncv}
\moderncvcolor{blue}
\moderncvstyle{banking}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[scale=0.8]{geometry}
\AtBeginDocument{\recomputelengths}

\firstname{Arturo}
\familyname{Veras Olivos}
\title{Curriculum Vitae}
\address{}{}
\mobile{+56 9 82413883}
\email{a.veras@gmail.com}

\begin{document}
\maketitle

\section{Profile}
I'm a goal-driven problem solver with a knack for aligning solutions with team objectives. My self-taught, curious nature and quick learning ability allow me to adapt easily to diverse work environments. I thrive on challenges, viewing them as opportunities for growth. I maintain good physical condition to ensure peak performance in all my tasks.

\section{Experience}
\subsection{Professional Position}
\cventry{2 years  11 months /  Agosto 2021 - Present}{Firmware and Software Developer}{Uqomm 
 (\url{www.uqomm.com})}{Con Con, Chile}{}{
As a Firmware Developer, I have been responsible for designing and programming firmware for STM32 Cortex M0 microcontrollers. This firmware is used to control radiofrequency equipment. In my role as a Backend Developer, I have developed and overseen software for monitoring radiofrequency equipment measurements using open-source software. Additionally, I have experience in server administration, maintaining servers on both Google Cloud and local servers to ensure smooth operations.
}

\cventry{4 years 2 months / July 2017 - August 2021}{Hardware Engineer}{BlackGPS 
 (\url{www.blackgps.com})}{Santiago, Chile}{}{
As a Design and Hardware Engineer, I was responsible for designing, manufacturing, programming, testing, and commissioning a device to prevent truck theft using GNSS and GSM signal jammers.
\\
In my role as Hardware Support, I configured and supported hardware for fleet control and management, particularly devices from brands like Teltonika, DCT Syrus, and ERM Starlink.
\\
As a BackEnd Developer, I developed new features on the server, processing information from tracking devices using SpringBoot in Java to integrate CANBus data from trucks into the server via cellular.
\\
In my capacity as a Flutter developer, I implemented new functionalities in the mobile app using Flutter, established Bluetooth communication with the tracking device, and improved the user interface.
}

\cventry{11 months / January 2017 to November 2017}{Electronic Engineer}{Prosismic SpA}{Viña del Mar, Chile}{}{
As an Electronic Engineer, I developed a functional prototype for commercial validation of 80 devices that would be part of an early earthquake sensor network using a Photon Wifi IoT board from Particle.
}

\cventry{7 month / June 2016 - December 2017}{Founder}{Deuterio - Hydrogen Generators}{Viña del Mar}{Chile}{
A project called Deuterio emerged from the EPS project, focusing on developing new hydrogen generation technology. As a Commercial Director, I was responsible for seeking financing through public or private instruments and generating business models for projects. In my role as a Researcher, I conducted research in electrochemistry, focusing on designing and developing prototypes for efficient oxyhydrogen gas generation. Lastly, as an Electronic Developer, I participated in microcontroller programming for signal generation and assembly of electronic test benches.}

\cventry{7 month / January 2016 - July 2016}{Technical Director}{EPS Project}{Viña del Mar, Chile}{}{The project aimed to build a hydrogen generator using three innovative technologies: pulsed electrolysis, photolysis with UV rays, and sonolysis with high-frequency electric piezoelectric transducers. My responsibilities included coordinating, planning, executing, and supervising teams in the areas of Electronics, Chemistry, Design, and Sales for an R&D project funded by CORFO's Innova department. As an Electronics developer, I programmed a microcontroller to generate a variable pulse train in frequency and duty cycle necessary to excite the electrolyzer, and conducted efficiency tests on a power generator.}

\cventry{6 month / July 2015 - December 2016}{Electronic Engineer}{HH Motors Project}{Valparaíso, Chile}{}{Focused on researching, energy efficiency testing, analysis, and validation of an alkaline electrolyzer. Designed and implemented a circuit to modify the electronic fuel injection system of a vehicle, conducting fuel performance tests.}

\cventry{2 month / January 2014 - Febraury 2014}{Research Intern}{Scientific Technological Center Valparaíso}{Valparaíso, Chile}{}{Responsible for researching and developing a device that would allow a GPU to be connected to a PC via a common interface such as USB or Ethernet, enabling the execution of Parallel Computing applications. During my research, I evaluated different alternatives and presented a detailed report covering information about various devices, their features, advantages, disadvantages, and prices. More details about my project can be found here: \url{https://github.com/mavillan/proyectoRpi}.}

\cventry{2 month / December 2012 - January 2013}{Intern Programmer}{Laboratory of Instrumentation and Photonics}{Santiago , Chile}{}{Programmed a Xilinx Virtex-5 XC5VLX110T-1FF1136 FPGA using LabVIEW and Python modules. I was responsible for installing all the necessary modules for the FPGA to function properly, involving error detection and correction, meeting dependencies, and fixing the code.}

\cventry{2 month / January 2009 - February 2010}{Research Intern}{Federico Santa María Technical University}{Valparaíso, Chile}{}{Tasked with researching the latest microcontrollers and development boards on the market to choose the next development kit for the electronics department's laboratory course. Also responsible for maintaining a website displaying all the job offers from the electronics department, updating the information based on received emails.}

\subsection{Other Jobs}
\cventry{January 2015 - March 2015}{Administrative Assistant}{Bottai SA.}{Arica, Chile}{}{Conducted tests for quality control of different types of concrete.}

\cventry{October 2013 - November 2013}{Salesperson}{Entel}{Valparaíso, Chile}{}{Directly door-to-door selling Entel products for households, including internet, satellite television, and telephony.}

\section{Education}
\cventry{2006--2014}{Electrical Engineer - Computers Major}{Federico Santa María Technical University}{Valparaíso, Chile}{}{}
\section{Thesis}
\cvitem{Title}{\emph{Implementation of a Path Generator in a Navigation System for a Cognitive Mobile Robot}}
\cvitem{Description}{Integrated a route generator into the Cognitive Memory and SLAM (Simultaneous Localization and Mapping) features of the mobile robot IRMA-III to enable autonomous movement in search of a target.}


\newpage
\section{Management and Interpersonal Skills}
\cvitem{Technical Experience}{Firmware and software development, basic electronic circuit design, technology integration.}
\cvitem{Project Management}{Coordination of cross-functional teams to achieve objectives.}
\cvitem{Innovation}{Participation in the development of new technologies and features.}
\cvitem{User-Centered Approach}{Consideration of user needs and experiences in product development.}
\cvitem{Adaptability}{Ability to quickly learn and adapt to changes in products and industries.}

\section{Technical Skills}
\cvcomputer{\textbf{Programing Languages}}{C, C++,Java, Python}{\textbf{Networking \& Communications}}{TCP/IP, LoRa, GPS, I2C, SPI}
\cvcomputer{\textbf{Scripting}}{Bash, Ansible}{\textbf{Version Control}}{Git}
\cvcomputer{\textbf{Frameworks}}{STM32, Google Cloud: Compute Engine, Flutter, FreeRTOS, Open Source}



\section{Languages}
\cvitem{Spanish}{Native}
\cvitem{English}{Advanced Reading, Intermediate Speaking}

\section{Contests and Workshops}

\cventry{November 2022}{HoruS Management Strategy}{Agile Methodologies Training}{Uqomm}{}{}{}
\cventry{July 2019}{Powered by eClass}{Agile Development: Scrum + Kanban}{BlackGps}{}{}{}
\cventry{January 2017}{Summer School}{Analog Integrated Circuit Design}{Synopsys - UTFSM}{}{}{}
\cventry{August 2015}{Winner of I+D Applied Contest with HH Motors project}{Apply Your Idea}{Copec UC Foundation}{}{}
\cventry{October 2015}{Contest-Exhibition of Technological Projects}{EXPOTEC}{UTFSM}{}{}

\end{document}
